Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-11-16 robdml.tex
tex
comment appendix

Apart from that, our method outperforms the previous methods in every important
aspect, \ie, ERS, training cost (efficiency), and R@1, as shown in
\cref{tab:sota}.
%
HM[$\mathcal{R},\mathcal{M}$] and HM[$\mathcal{R},g_\mathsf{LGA}$] can reach a
higher ERS, but are excluded from comparison due to significant performance
drop in R@1.

@@

Adversarial robustness is crucial for DML applications.
%
In this paper, we improve adversarial training efficiency through HM.
%
Since regular training and the min-max adversarial training can be expressed as
two boundary cases of HM, Graduate Adversary has been demonstrated effective as
an ``intermediate point'' between the two cases.
%
Enforcing the previously neglected Intra-Class Structure can further improve
model robustness and adversarial training efficiency.
%
%Our method outperforms previous methods.

@@

\input{appendix.tex}

>>>>

In most cases, our method outperforms the previous methods in every important
aspect, \ie, ERS, training cost (efficiency), and R@1, as shown in
\cref{tab:sota}.
%
HM[$\mathcal{R},\mathcal{M}$] and HM[$\mathcal{R},g_\mathsf{LGA}$] can reach a
higher ERS, but are excluded from comparison due to significant performance
drop in R@1.

@@

%Adversarial robustness is crucial for applications.
%
In this paper, HM efficiently and flexibly creates adversarial examples for
adversarial training;
%
LGA specifies an ``intermediate'' destination hardness for balancing robustness
and performance on benign examples;
%
ICS loss term further improves model robustness.
%
The state-of-the-art defenses have been surpassed in terms of overall performance.

@@

%\input{appendix.tex}
